SAT Solving for Vesicle Traffic Systems in Cells

### 2017-07-20 paper/bio_MTedit.tex
push

If a VTS is $k$-connected, every pair of compartments remain reachable after dropping $k-1$ vesicles. In principle the connectivity of a VTS can be determined by cell-biological studies.
\ankit{Why $k$-connected matters?}
% We have previously shown \cite{shukla} that a feasible VTS must be at least 3-connected but might need to have higher connectivity. 
Here we have build a tool that studies properties of VTSs that are not $k$-connected, from some $k$. 
%We later will discuss conditions of maximum connectivity [or LGC, least guarantee connectivity] and minimal connectivity [or LRC, least required connectivity].

>>>>

If a VTS is $k$-connected, every pair of compartments remain reachable
after dropping $k-1$ vesicles.
%
This property of VTSs have been considered informative and
studied~\cite{shukla}.
%
Here we have build an \emf{efficient} tool that studies properties of
VTSs that are not $k$-connected, from some $k$.

### 2017-07-20 paper/encoding.tex
minor
pass
push

In this section, we will formally define VTSs as a labeled graph
and the conditions on the graphs that are discussed in the previous
section.
%
Subsequently, we will present the SAT encoding of the search problems
for the graphs that satisfies the conditions.

@@

\paragraph{Search problem}
Based upon earlier discussion, we need to answer the following search
question among VTSs.
For a given $k$, size $\nu$, and molecule number $\mu$,
we are searching for well-structured, stable, and well-fused VTS
$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
$|\nodes| = \nu$, $|\mols = \mu|$, and
$G$ is not $k$-connected.

>>>>

In this section, we will formally define VTSs as a labeled graph
and the conditions on the graphs that are discussed in the previous
section.
%
Subsequently, we will present the SAT encoding of the search problems
for the graphs that satisfy the conditions.

@@

\paragraph{Search problem}
Based upon earlier discussion, we need to answer the following search
question among VTSs.
For a given $k$, size $\nu$, and molecule number $\mu$,
we are searching for well-structured, stable, and well-fused VTS
$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
$|\nodes| = \nu$, $|\mols| = \mu$, and
$G$ is not $k$-connected.
